\paperTitle

### 2014-05-12 doc/icml2014/directed.tex
read up to undirected model

From \citet{anandkumar13tensor} given the non-degeneracy assumptions
  \assumptionref{non-degeneracy}, we have that $\mOpphat{v}{i}$
  converges to $\mOpp{v}{i}$ at a rate of $n^{-\frac12}$ with a constant
  that depends polynomially on the $k$-th singular value of
  $\mOpp{v}{i}$:
\begin{theorem}[Sample complexity for $\mOpp{v}{i}$]
  \label{thm:sample-complexity}
  Wlog, let $v=1$ and $i=1$. Let $x_1, x_2, x_3$ be three views for
  $h_1$. With probability at least $1 - \delta$,
\begin{align*}
  \|\mOpphat{1}{1} - \mOpp{1}{1}\|_F 
    &\le  \\
    &
      O\left(
      \frac{k \log(1/\delta) {\pi\oft{1}}_{\max}/{\pi\oft{1}}_{\min} } 
      {\sqrt{n}(\sigma_{k}(\mOpp{1}{1}) \sigma_{k}(\mOpp{1}{2}))^{5/2}} \right) \epsilon.
\end{align*}

@@

In general, $\sigma_{k}(\mOpp{v}{i})$ can depend exponentially on the
  path length between the hidden variable $h_i$ and $x_v$.
This is expected because the influence from $h_i$ to $x_v$
  gets diluted for every latent variable it must factor through.

>>>>

From \citet{anandkumar13tensor} given the non-degeneracy assumptions
  \assumptionref{non-degeneracy}, we have that $\mOpphat{v}{i}$
  converges to $\mOpp{v}{i}$ at a rate of $n^{-\frac12}$ with a constant
  that depends polynomially on the $k$-th singular value of
  $\mOpp{v}{i}$:
\begin{theorem}[Sample complexity for $\mOpp{v}{i}$]
  \label{thm:sample-complexity}
  Without loss of generality, let $v=1, i=1$, and let $x_1, x_2, x_3$ be three views for
  $h_1$. With probability at least $1 - \delta$,
\begin{align*}
  \|\mOpphat{1}{1} - \mOpp{1}{1}\|_F 
    &\le  \\
    &
  \hspace{-0.3in}
      O\left(
      % PL: remove pi_max because that's upper bounded by 1.
      \frac{k \log(1/\delta) } 
      {\sqrt{n} \, \pi\oft{1}_{\min} (\sigma_{k}(\mOpp{1}{1}) \sigma_{k}(\mOpp{1}{2}))^{5/2}} \right) \epsilon,
\end{align*}
where $\pi\oft{1}_{\min}$ is the smallest element of $\pi\oft{1}$.
\todo{what's $\epsilon$?}

@@

% PL: we don't have a crisp theorem (because there's multiple paths), so leave it vague.
Note that $\sigma_{k}(\mOpp{v}{i})$ can become extremely
small if $h_i$ and $x_v$ are connected via many intermediate hidden variables.
\todo{cite work - Sontag?}
%In general, $\sigma_{k}(\mOpp{v}{i})$ will depend exponentially on the
  %path length between the hidden variable $h_i$ and $x_v$.
%This is expected because the influence from $h_i$ to $x_v$
  %gets diluted for every latent variable it must factor through.
